\setlength{\parskip}{.7ex}
\vspace*{0.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The {\bf Joint Conference on Lexical and Computational Semantics (*SEM)} provides a forum of exchange for the growing number of NLP researchers working on different aspects of semantic processing.
After the previous editions of *SEM in Montreal (2012), Atlanta (2013), and Dublin (2014), the 2015 edition will take place in Denver on June 4 and 5 and is colocated with SemEval and NAACL. As in 2014 at COLING, also on this occasion *SEM and SemEval chose to coordinate their programs by featuring a joint invited talk.
In this way, *SEM aims to bring together the ACL SIGLEX and ACL SIGSEM communities.

The acceptance rate of *SEM 2015 was quite competitive: out of 98 submissions,
we accepted 36 papers for an overall acceptance of 37\%. The acceptance rate of long paper that were accepted for oral presentation (18 out of 62) is 29\%. The papers cover a wide range of topics including distributional
semantics; lexical semantics and lexical acquisition; formal and linguistic semantics; discourse semantics;
lexical resources, linked data and ontologies; semantics for applications; and extra-propositional semantics: sentiment and figurative meaning.

The *SEM 2015 program consists of oral presentations for selected long papers and a poster session for long and short papers.

\vspace{1mm}

{\bf Day One, June 4th:}
\begin{itemize}
  \item Joint *SEM SemEval keynote talk by {\bf Marco Baroni};
  \item Oral presentation sessions on distributional semantics, lexical semantics, and extra-propositional semantics;
  \item Poster session.
\end{itemize}

{\bf Day Two, June 5th:}
\begin{itemize}
  \item Keynote talk by {\bf Preslav Natkov};
  \item Oral presentation sessions on semantics for applications, lexical resources and ontologies, formal semantics, and discourse semantics;
  \item *SEM Best Paper Award.
\end{itemize}

We cannot finish without saying  that *SEM 2015 would not have been possible without the considerable efforts of our area chairs,
their reviewers, and the computational semantics community in general.

We hope you will enjoy *SEM 2015,

\vspace{4mm}

\noindent Martha Palmer, University of Colorado Boulder, General Chair\\ 
\noindent Gemma Boleda, University of Trento, Program Co-Chair\\
\noindent Paolo Rosso, Universitat Polit{\`e}cnica de Val{\`e}ncia, Program Co-Chair\\
