\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

Thank you so much for joining us in Copenhagen!  Welcome to a cosmopolitan city of fantastic restaurants, lovely seascapes, rich history, and lots and lots of cyclists! 

We have an exciting program lined up for you, with three Invited talks, fifteen workshops, seven tutorials, nine TACL presentations, 322 reviewed papers presented as both oral talks and posters, and twenty-one demos.  I am especially grateful to our Program Chairs, Rebecca Hwa and Sebastian Riedel, who did a fantastic job managing a backbreaking 1,500 paper submissions (1466 reviewed papers).  This involved 51 Area chairs and 980 reviewers.  We tried some new things this year (never conducive to a smooth process) including a more careful handling of the COIs that result from Area Chair submissions, and the addition of a meta-review step to encourage more thoughtful reviewing.  We are soliciting feedback on the meta-review process, from both reviewers and authors.  Despite the additional time involvement, many of the Area Chairs embraced this new approach, and would like to repeat it. However, there are clearly a few dissenters, since Rebecca and Sebastian ended up writing around 200 meta-reviews themselves at the last minute!  We are also trying to raise the visibility and status of the poster sessions by integrating them as parallel sessions alongside oral talks, with poster session chairs.  This is in response to the survey results from EMNLP 2015 that indicated a decided preference for smaller, more frequent poster sessions during the day rather than evening mega-sessions.  Finally, Rebecca and Sebastian are bringing you three outstanding invited speakers, Dan Jurafsky, Sharon Goldwater, and Nando de Freitas.   No program chairs ever worked harder to bring you a superb set of presentations in an attendee friendly setting.

I am also very grateful to Victoria Fossum and Karl Moritz Hermann, our Workshop Chairs, who put together a terrific slate of fifteen workshops, and paid meticulous attention to ensuring that each workshop could hold exactly the poster sessions, invited talks and special events that it required.  Our tutorial chairs, Alexandra Birch and Nathan Schneider, also outdid themselves, providing especially tempting tutorial offerings.  Matt Post deserves to be singled out, for being an Advisor to our conscientious and successful Handbook Chair, Joachim Bingel, as well as becoming a welcome last minute addition to our excellent team of Demo Chairs, Lucia Specia and Michael Paul.  Thanks are due to our Website Chair, Anders Johannsen, who responded promptly and deftly to all of our requests, and to our Student Volunteer and Student Sponsorship Chairs, Zeljko Agic and Yonatan Bisk, who brought you the helpful and energetic volunteers who keep things running smoothly.

Last but not least, many thanks to your hosts, our Local Arrangements Chairs, Dirk Hovy and Anders Søgaard and their team.  Their concern has been increasing the enjoyment of your experience, and to that end they proposed a stunning venue, put together an amazing reception and Social Event, chose your conference bags, issued all the invitation letters for visas, helped create all the signs, etc., etc., etc.  Dan Hardt, our Sponsorship chair, working with Anders and Dirk, raised an unusual amount of local sponsorships, all to defray the cost of the Social Event.

As always, we are extremely indebted to our generous sponsors. Our platinum sponsors are Google, Amazon, Baidu, Apple, Facebook, Bloomberg and Siteimprove.  Gold sponsors include IBM Research, Microsoft, eBay, SAP, Textkernel, Maluuba, Zalando, Recruit Institute of Technology and Deloitte.  Silver sponsors are Nuance, Oracle, Sogou, Huawei, Duolingo, CVTE, Unsilo and Wizkids. Snap Inc., Grammarly and Yandex are our Bronze sponsors.

Finally, many, many thanks to our Area Chairs, our reviewers, and our authors, whose outstanding research is being showcased here for your delectation. \textit{Nyd det mens det varer!}

\vspace{3em}
\noindent
Best Regards,\\
Martha Palmer\\
EMNLP 2017 General Chair



\index{Palmer, Martha}
